Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Find or prove?
Slightly smaller picture

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}[scale=0.33]%{{{
        \begin{scope}
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 10) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 8) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 8) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Md) at (4, 8) {\phantom{0}};

@@

        \begin{scope}[xshift=15cm]
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
            \node [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
            \node [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
            \node [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
            \node [above = 0 of Ma4, font=\small] { \vphantom{0}4 };

            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Ma1.north west) -- (Ma4.north east)
            node [midway, above=0.7cm] { $a \mapsto$ };

@@

            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mc2) at (4.2, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
            \node [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
            \node [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
            \node [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
            \node [below = 0 of Mc4, font=\small] { \vphantom{0}4 };

            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Mc4.south east) -- (Mc1.south west)
            node [midway, below=0.7cm] { $c \mapsto$ };

@@

            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Md4.north east) -- (Md1.south east)
            node [midway, right=0.7cm] { $d \mapsto$ };

@@

>>>>

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}[scale=0.33]%{{{
        \begin{scope}
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma) at (2, 8) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 6) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 6) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Md) at (4, 6) {\phantom{0}};

@@

        \begin{scope}[xshift=15cm, yshift=-1cm]
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
            \node (La1) [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
            \node (La2) [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
            \node (La3) [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
            \node (La4) [above = 0 of Ma4, font=\small] { \vphantom{0}4 };

            \node [left=0 of La1] { $a \mapsto \{$ };
            \node [right=0 of La4] { $\}$ };

@@

            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mc2) at (4.2, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
            \node (Lc1) [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
            \node (Lc2) [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
            \node (Lc3) [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
            \node (Lc4) [below = 0 of Mc4, font=\small] { \vphantom{0}4 };

            \node [left=0 of Lc1] { $c \mapsto \{$ };
            \node [right=0 of Lc4] { $\}$ };

@@

            \draw [decorate, decoration={brace, raise=0.5cm}, very thick] (Md4.north east) -- (Md1.south east)
            node [midway, right=0.7cm] { $\reflectbox{\ensuremath{\mapsto}} d$ };

@@

?? Time to find or time to prove? Can we figure this out?
